\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-24 manuscript.Rnw
Updates to references

\subsection{Partitioned survival models} \label{sec:PSMs}
PSMs are conceptually similar to STMs in that they are characterized by mutually exclusive health states. They differ, however, in that state probabilities are not computed via matrix multiplication or individual simulation, but from a set of non-mutually exclusive survival curves \citep{glasziou1990quality, woods2018nice}. Each survival curve represents time to transition to that state or to a more severe health state.

>>>>

\subsection{Partitioned survival models} \label{sec:PSMs}
PSMs are conceptually similar to STMs in that they are characterized by mutually exclusive health states. They differ, however, in that state probabilities are not computed via matrix multiplication or individual simulation, but from a set of non-mutually exclusive survival curves \citep{glasziou1990quality, woods2017nice}. Each survival curve represents time to transition to that state or to a more severe health state.
